---
jupyter:
  jupytext:
    formats: ipynb,Rmd
    text_representation:
      extension: .Rmd
      format_name: rmarkdown
      format_version: '1.1'
      jupytext_version: 1.2.4
  kernelspec:
    display_name: R
    language: R
    name: ir
---

# Forward vs. backward contact tracing
Figures show the estimated effectiveness of forward and backward contact tracing. Left panels (A, D, G): the effectiveness (the proportion of generation 3 cases averted) of forward tracing alone; middle panels (B, E, H): the effectiveness of a combination of forward and backward tracing; right panels (C, F, I): additional effectiveness by combining backward tracing with forward tracing. Colours represent the relative reduction in infectiousness of generation 3 cases if traced and put in quarantine.

```{r}
source("basic_funcs.R") # load functions
#options(jupyter.plot_mimetypes = "image/svg+xml")
```

```{r}
par(mfrow=c(3,3),mar=c(4,3,2.5,1),mgp=c(2,0.6,0),las=0,yaxs="i")

tertiary<-plotbypc(R=1.2,k=0.2,q=0.8,d=0.2, panel=c("(A)","(B)","(C)"))
tertiary<-plotbypc(R=1.2,k=0.2,q=0.5,d=0.2, panel=c("(D)","(E)","(F)"))
tertiary<-plotbypc(R=1.2,k=0.5,q=0.8,d=0.2, panel=c("(G)","(H)","(I)"))
```

```{r}
par(mfrow=c(3,3),mar=c(4,3,2.5,1),mgp=c(2,0.6,0),las=0,yaxs="i")

tertiary<-plotbypc(R=2.5,k=0.2,q=0.8,d=0.2, panel=c("(A)","(B)","(C)"))
tertiary<-plotbypc(R=2.5,k=0.2,q=0.5,d=0.2, panel=c("(D)","(E)","(F)"))
tertiary<-plotbypc(R=2.5,k=0.5,q=0.8,d=0.2, panel=c("(G)","(H)","(I)"))
```

```{r}
par(mfrow=c(3,3),mar=c(4,3,2.5,1),mgp=c(2,0.6,0),las=0,yaxs="i")

tertiary<-plotbypc(R=1.2,k=0.2,q=0.8,d=0.5, panel=c("(A)","(B)","(C)"))
tertiary<-plotbypc(R=1.2,k=0.2,q=0.5,d=0.5, panel=c("(D)","(E)","(F)"))
tertiary<-plotbypc(R=1.2,k=0.5,q=0.8,d=0.5, panel=c("(G)","(H)","(I)"))
```

```{r}

```
